Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-05 paper.tex
Added chord diagram interaction & colour coding details

The chord diagram is a visualisation technique based on the node-link metaphor that arranges nodes along the circumference of a cirle. 
Each node is represented by an arc where its length is proportional to the total volume of incoming and outging flows. 
Chords or curved line segements are drawn to connect nodes. 
The width at the head or tail of each chord indicates the amount of movement that occured between a certain location to another at the other end.

>>>>

The chord diagram is a visualisation technique based on the node-link metaphor that arranges nodes along the circumference of a cirle. 
Each node is represented by an arc where its length is proportional to the total volume of incoming and outging flows. 
Chords or curved line segements are drawn to connect nodes. 
The width at the head or tail of each chord indicates the amount of movement relative frequency of movement from a certain location to another. 
In our implementation, nodes are colour coded to indicate individual provinces and the major cities located within their administrative boundaries. 
Interactive filtering is introduced to simplify the visualisation and details are provided in popup dialogue when upon mouse-over.
